Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-08 appendix.tex
tex

@@

Adversarial training requires more time and GPU memory than regular training.
%
The adversarial training of ResNet-18 with our method requires about 7\~{}10GB
of memory per GPU in distributed data parallel mode, which is affordable to
most researchers in the community.
%
Adversarial training of ResNet-50 requires much more than 12GB of memory per
GPU, which will make it harder for some readers to reproduce the results
and compare.

@@

\noindent\textbf{I. Training Cost}

@@

For reference, the adversarial training cost of RN18 with two Nvidia Titan Xp
GPUs in terms of wall time is summarized in
%
\oo{todo}

~\newline
\noindent\textbf{II. Complete Results for Tab.~2 in Manuscript}

@@

@@

 [T] Face recognition methods such as ArcFace can be used for
	metric learning.
	%
	Is defense for face recognition missing from the literature?

 [T] Unsup learning with DML robustness.

>>>>

\section*{Supplementary Material}

In this supplementary material, we provide further technical details and
discussions that are not included in the manuscript due to space limit.
%
Discussions required by the author guidelines can also be found in this
supplementary material.

@@

Adversarial training requires more time and GPU memory than regular training.
%
The adversarial training of ResNet-18 with our method requires about 7\~{}10GB
of memory per GPU in distributed data parallel mode.
%
%Adversarial training of ResNet-50 requires much more than 12GB of memory per
%GPU, which will make it harder for some readers to reproduce the results
%and compare.

@@

\noindent\textbf{I. Detailed Interpretation of Experimental Results}

\ul{(1) Table.~1: ``Mean \& Variance ...'''}

\ul{(2) Table.~2: ``... Source \& Destination Hardness ...''}

\ul{(3) Table.~3: ``Hardness Manipulation ...'' and Fig.~6}

\ul{(4) Table.~4: ``... Graduate Adversary ...'' and Fig.~7}

\ul{(5) Table.~5: ``Intra-Class Structure ...'' and Fig.~8}

\ul{(6) Table.~6: ``... State-of-The-Art ...''}

~\newline
\noindent\textbf{II. Training Cost}

@@

For reference, the most time-consuming experiment is
HM[$\mathcal{S},g_\mathsf{LGA}$] on the SOP dataset.
%
When $\eta=8$, the experiment takes $32$ hours with two Nvidia Titan Xp GPUs;
%
When $\eta=32$, the experiment takes $105$ hours with two Nvidia Titan Xp GPUs.

~\newline
\noindent\textbf{III. Complete Results for Tab.~2 in Manuscript}

@@

~\newline\textbf{IV. DML \& Classification}

It is unknown how defense methods for DML relates to the classification defense
task.
%
DML is closely related to self-supervised learning.
%
It is also unknown if a defense for the supervised learning scenario will
inspire the defense for unsupervised robust feature learning.

@@
